Random Forests", OAs

### 2024-02-08 src/oa_RF.Rmd
oa rf

```{r}
# create a list of the above model outputs
filenames <- list.files(paste0(path, "/outputs/rf/models/oa_rf/regions"), pattern = "*.RData", full.names = T)

@@

@@

df.predictions <- data.frame()
for (i in regions){
  #for (j in regions[!regions == i]){
    pred <- predict(fit.model.all[names(fit.model.all)==paste0("region_", i)], 
                    df[df$RGN11CD==i,])
    pred <- as.data.frame(pred)
    rownames(pred) <- c()
    assign(paste0("region.predict.model.", ".on.", i), pred)

@@

    #***dplyr::select(RGN21CD, ladcd, year, growth, 1)***

    d <- d[,c(5, 2, 4, 6, 1)]     
    colnames(d)[5] <- "predictions"
    d <- d %>% mutate(trained.on = i)
    df.predictions <- rbind(d, df.predictions)
  #}
}

@@

>>>>

```{r, eval=F}
# create a list of the above model outputs
filenames <- list.files(paste0(path, "/outputs/rf/models/oa_rf/regions"), pattern = "*.RData", full.names = T)

@@

```{r, eval=F, include=TRUE, results= 'markup', message=FALSE}
lapply(names(fit.model.all), function(x) plot(varImp(fit.model.all[[x]]), main=as.character(x)))
```

```{r, eval=F}
help <- lapply(fit.model.all, function(x) varImp(x)) 
help <- lapply(help, function(x) x[[1]])
help <- do.call("rbind", help)

@@

new.path <- "/hdd/tmp/regions/"
#filenames <- list.files(paste0(path, "/outputs/rf/models/oa_rf/regions"), pattern = "*.RData", full.names = T)

df.predictions <- data.frame()

for (i in regions){
  load(file = paste0(new.path, "region_", as.character(i), ".RData"))
  #model.name <- gsub("/home/nw19521/projects/web.diffusion/outputs/rf/models/oa_rf/regions/|.RData", "", i)
  #assign(as.character(i), model.all)

  pred <- predict(model.all, df[df$RGN11CD==i,])
  pred <- as.data.frame(pred)

  rownames(pred) <- c()
  assign(paste0("region.predict.model.", ".on.", i), pred)

@@

  d <- d %>% dplyr::select(RGN11CD, oa11cd, year, n, pred)

  colnames(d)[5] <- "predictions"
  d <- d %>% mutate(tested.on = i)
  df.predictions <- rbind(d, df.predictions)

  rm(model.all)
}

# df.predictions <- data.frame()
# for (i in regions){
#   #for (j in regions[!regions == i]){
#     pred <- predict(fit.model.all[names(fit.model.all)==paste0("region_", i)], 
#                     df[df$RGN11CD==i,])
#     pred <- as.data.frame(pred)
#     rownames(pred) <- c()
#     assign(paste0("region.predict.model.", ".on.", i), pred)
#     
#     d <- paste0("region.predict.model.", ".on.", i)
#     d <- cbind(get(d), df %>% filter(RGN11CD==i)) #%>% arrange(year, ladcd)
#     
#     #***dplyr::select(RGN21CD, ladcd, year, growth, 1)***
#     
#     d <- d[,c(5, 2, 4, 6, 1)]     
#     colnames(d)[5] <- "predictions"
#     d <- d %>% mutate(trained.on = i)
#     df.predictions <- rbind(d, df.predictions)
#   #}
# }

df.predictions <- df.predictions %>% mutate(test.train = paste0(RGN11CD, ".", tested.on))

# split to list by region pair
pred.by.region.all.list <- split(df.predictions, df.predictions$test.train)

@@

path.lookup <- paste0(path, "/data/raw/Local_Authority_District_to_Region_(April_2021)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup) %>% 
  dplyr::select(RGN21CD, RGN21NM) %>% 
  distinct() %>% 
  rename(RGN11CD = RGN21CD) %>% 
  add_row(RGN11CD = c("Scotland", "NI", "Wales"), 
          RGN21NM = c("Scotland", "Nortern Ireland", "Wales"))

path.out <- paste0(path, "/outputs/rf/figures/test_regions_OA.csv")
rf.year.all.metrics %>% 
  as.data.frame() %>%
  rownames_to_column(var = "metrics") %>% 
  pivot_longer(!metrics, names_to = "train.test") %>% 
  pivot_wider(names_from = metrics, values_from = value) %>% 
  separate(train.test, c("train", "test"), remove = F) %>% 
  # left_join(lookup.region, by = c("train" = "RGN11CD")) %>% 
  # rename(train.region=RGN21NM) %>% 
  left_join(lookup.region, by = c("test" = "RGN11CD")) %>% 
  rename(test.region=RGN21NM) %>% 
  arrange(Rsquared) %>% 
  dplyr::select(test.region, Rsquared) %>% 
  write_csv(path.out)
```
